Measuring Software Ticket Quality using Statistical Analysis

### 2018-04-17 paper/paper.tex
Complete abstract section

\begin{abstract}

\end{abstract}

@@

This paper outlines the standard template for an MSci submission.
In earlier years, MSci students at the School of Computing
Science\footnote{\url{http://www.dcs.gla.ac.uk}},
University of Glasgow, were expected to produce a full-length
dissertation. Now, the requirement is for MSci students to
write a paper of up to 14 pages in length, using the supplied
\texttt{mpaper} \LaTeX style file.

@@

Again, Simon Peyton Jones has a lovely description of how to write a
paper on his
website\footnote{\url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}}.
Personally, I put URLs in footnotes and \emph{bona fide} references
in the bibliography. For instance, Turing \cite{turing37computable}
and Knuth \cite{knuth68art} would not be out of place in list of
references.
How many references? Hard to say. Five is not enough, 50 is pushing
it.

@@

\begin{quotation}
 The Assyrian came down like the wolf on the fold,
 And his cohorts were gleaming in purple and gold;
 And the sheen of their spears was like stars on the sea,
 When the blue wave rolls nightly on deep Galilee.

 Like the leaves of the forest when Summer is green,
 That host with their banners at sunset were seen:
 Like the leaves of the forest when Autumn hath blown,
 That host on the morrow lay withered and strown.
\end{quotation}

>>>>

\begin{abstract}
Software tickets are of valuable importance to the whole computing science 
field - they guide engineers towards better planning, management 
and tracking of their progress throughout complex projects. However, there
are few studies that investigate what makes for a high quality,
valuable ticket. This can lead to multiple issues in a company, such as 
increased communication friction between developers and end users filing bug
reports, as well as increased overall costs due to waste of development effort. 
In this research paper, we present our findings after 
investigating a large number of variables surrounding software tickets, 
such as whether the presence of stack traces influence the time 
to close for the ticket. Our results show that the presence and type of attachments,
comments complexity (i.e. number of comments per ticket), grammar correctness scores
as well as the sentiment drawn from the comments can influence the quality of the ticket.
We bring a couple of novel aspects to the research
community including one of the largest dataset statistically analysed in the field,
as well as state-of-the-art sentiment and grammar correctness analysis.
\end{abstract}

@@

This paper outlines the standard template for an MSci submission.
In earlier years, MSci students at the School of Computing
Science,
University of Glasgow, were expected to produce a full-length
dissertation. Now, the requirement is for MSci students to
write a paper of up to 14 pages in length, using the supplied
\texttt{mpaper} \LaTeX style file.

@@

Again, Simon Peyton Jones has a lovely description of how to write a
paper on his
website.
Personally, I put URLs in footnotes and \emph{bona fide} references
in the bibliography. For instance, Turing \cite{turing37computable}
and Knuth \cite{knuth68art} would not be out of place in list of
references.
How many references? Hard to say. Five is not enough, 50 is pushing
it.

@@
